---
title: "JMJPFU-angryTemplate"
output: html_notebook
---

# JMJPFU
## 24-Feb-2017

This is a template for the Angry Template. Let us proceed with the required steps.


### Step 1: Loading the required library files

```{r}
library(SnowballC)
library(RWeka)
library(rJava)
library(RWekajars)
library(tm)
```


### Step 2: Looking at the data

```{r}
angryRev <- angryDf$badRev
angryRev[1:6]
```

### Step 3 : Creating the term Document Matrix

This step is only required for the first time a template is created

```{r}
 angTdm <- tdmCreator(angryRev)
```

### Step 4 : Creating an initial template for the emotion

This step is also required to be done for the first time a template is created

```{r}
roomAngTemp <- templateCreate(angTdm,'rooms',0.30)
```

### Step 5 : Expanding the template

This is the step which needs to be followed once an intial template is created

```{r}
roomAngTemp <- conTemplate(angryRev,1,6,"room","NA",0.3,"freq1",roomAngTemp)
```

#### Creating Template for Restaurant

## Initial template

```{r}
### Angry data

#angryRev

### Creating an initial template for the emotion

restAngTemp <- templateCreate(angTdm,'restaurant',0.05)

```

The angTdm dosent have any data pertaining to restaurants. So some more data has to be collected
