---
title: "JMJPFU-angryTemplate"
output: html_notebook
---

# JMJPFU
## 24-Feb-2017

## Artefacts for a hotel

Room: roomAngTemp
Food: restAngTemp
Restaurant: restAngTemp 
Staff: staffAngTemp 
Lobby: No data
Reception: receptionAngTemp  
Transfer:  transferAngTemp : no data
Facilities: facilityAngTemp : no data
Recommend: reccoAngTemp : no data

This is a template for the Angry Template. Let us proceed with the required steps.


### Step 1: Loading the required library files

```{r}
library(SnowballC)
library(RWeka)
library(rJava)
library(RWekajars)
library(tm)
```


### Step 2: Looking at the data

```{r}
angryRev <- angryDf$badRev
angryRev[1:8]
```

### Step 3 : Creating the term Document Matrix

This step is only required for the first time a template is created

```{r}
 angTdm <- tdmCreator(angryRev)
```

### Step 4 : Creating an initial template for the emotion

This step is also required to be done for the first time a template is created

```{r}
roomAngTemp <- templateCreate(angTdm,'rooms',0.30)
```

### Step 5 : Expanding the template

This is the step which needs to be followed once an intial template is created

```{r}
roomAngTemp <- conTemplate(angryRev,9,16,"rooms","NA",0.3,"freq3",roomAngTemp)
```

#### Creating Template for Food

## Initial template

```{r}
### Angry data

#angryRev

### Creating an initial template for the emotion

restAngTemp <- templateCreate(angTdm,'food',0.3)

## Subsequent template for food

restAngTemp <- conTemplate(angryRev,9,16,"food","NA",0.3,"freq2",restAngTemp)

```

# JMJPFU
### 28-Mar-2017

### Template Staff

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

angryRev <- angryDf$badRev

# Step 2 : Creating the initial tdm

 angTdm <- tdmCreator(angryRev[4]) # 4 is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 staffAngTemp <- templateCreate(angTdm,'staff',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

staffAngTemp <- conTemplate(angryRev,14,16,"staff","NA",0.3,"freq6",staffAngTemp)
```


### Template Reception

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

angryRev <- angryDf$badRev

# Step 2 : Creating the initial tdm

 angTdm <- tdmCreator(angryRev[13:16]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 receptionAngTemp <- templateCreate(angTdm,'reception',0.30)


```

### Process 2 : Adding on to the initial template


```{r}
# receptionAngTemp: This dosent have any data for process 2:

```

### Template Recommend

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

angryRev <- angryDf$badRev

# Step 2 : Creating the initial tdm

 angTdm <- tdmCreator(angryRev[1:16]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 reccoAngTemp <- templateCreate(angTdm,'reccomend',0.30)


```

### Process 2 : Adding on to the initial template


```{r}
# receptionAngTemp: This dosent have any data for process 2:

```

