---
title: "JMJPFU-Template"
output: html_notebook
---

# JMJPFU
### 29-Mar-2017

This is a template for Delight


## Artefacts for a hotel

Room: roomdelTemp
Food: resdelTemp
Restaurant: resdelTemp
Staff: staffdelTemp
Lobby: lobbydelTemp 
Reception: recepdelTemp
Transfer: trandelTemp
Facilities:facildelTemp
Recommend: reccodelTemp

### Initial tasks : Loading the library files

```{r}
library(SnowballC)
library(RWeka)
library(rJava)
library(RWekajars)
library(tm)

```


### Template 1 : Room

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

delightRev <- delightDf$badRev

# Step 2 : Creating the initial tdm

 delightTdm <- tdmCreator(delightRev[1:40]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 roomdelTemp <- templateCreate(delightTdm,'room',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

roomdelTemp <- conTemplate(delightRev,131,149,"room","rooms",0.3,"freq4",roomdelTemp)


```


# JMJPFU
### 29-Mar-2017 

### Template 2 : Food / Restaurant

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

delightRev <- delightDf$badRev

# Step 2 : Creating the initial tdm

 delightTdm <- tdmCreator(delightRev[1:40]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 resdelTemp <- templateCreate(delightTdm,'food',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

resdelTemp <- conTemplate(delightRev,131,149,"food","restaurant",0.3,"freq4",resdelTemp)


```


### Template 3 : Staff

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

delightRev <- delightDf$badRev

# Step 2 : Creating the initial tdm

 delightTdm <- tdmCreator(delightRev[1:40]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 staffdelTemp <- templateCreate(delightTdm,'staff',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

staffdelTemp <- conTemplate(delightRev,131,149,"staff","NA",0.3,"freq4",staffdelTemp)


```


### Template 4 : Lobby

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

delightRev <- delightDf$badRev

# Step 2 : Creating the initial tdm

 delightTdm <- tdmCreator(delightRev[1:40]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 lobbydelTemp <- templateCreate(delightTdm,'lobby',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

lobbydelTemp <- conTemplate(delightRev,131,149,"lobby","NA",0.3,"freq4",lobbydelTemp)


```

### Template 5 : Reception

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

delightRev <- delightDf$badRev

# Step 2 : Creating the initial tdm

 delightTdm <- tdmCreator(delightRev[1:40]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 recepdelTemp <- templateCreate(delightTdm,'reception',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

recepdelTemp <- conTemplate(delightRev,131,149,"reception","NA",0.3,"freq4",recepdelTemp)


```


### Template 6 : Transfer

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

delightRev <- delightDf$badRev

# Step 2 : Creating the initial tdm

 delightTdm <- tdmCreator(delightRev[1:40]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 trandelTemp <- templateCreate(delightTdm,'transfer',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

trandelTemp <- conTemplate(delightRev,131,149,"transfer","NA",0.3,"freq4",trandelTemp)

```


### Template 7 : Facilities

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

delightRev <- delightDf$badRev

# Step 2 : Creating the initial tdm

 delightTdm <- tdmCreator(delightRev[1:70]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 facildelTemp <- templateCreate(delightTdm,'facility',0.30)

```

### Process 2 : Adding on to the initial template


```{r}

facildelTemp <- conTemplate(delightRev,131,149,"facility","facilities",0.3,"freq3",facildelTemp)

```



### Template 8 : Reccomend

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

delightRev <- delightDf$badRev

# Step 2 : Creating the initial tdm

 delightTdm <- tdmCreator(delightRev[1:40]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 reccodelTemp <- templateCreate(delightTdm,'recommend',0.30)

```

### Process 2 : Adding on to the initial template


```{r}

reccodelTemp <- conTemplate(delightRev,131,149,"recommend","NA",0.3,"freq4",reccodelTemp)

```



