---
title: "JMJPFU-Template"
output: html_notebook
---

# JMJPFU
### 28-Mar-2017

This is the dissatisfied template for all artefacts

## Artefacts for a hotel

Room: roomdisTemp
Food: restdisTemp
Restaurant: restdisTemp
Staff: staffdisTemp
Lobby: 
Reception: 
Transfer: 
Facilities:
Recommend:

### Initial tasks : Loading the library files

```{r}
library(SnowballC)
library(RWeka)
library(rJava)
library(RWekajars)
library(tm)

```


### Template 1 : Room

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

dissatRev <- dissatDf$badRev

# Step 2 : Creating the initial tdm

 dissatTdm <- tdmCreator(dissatRev[1:6]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 roomdisTemp <- templateCreate(dissatTdm,'room',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

roomdisTemp <- conTemplate(dissatRev,10,11,"room","rooms",0.3,"freq2",roomdisTemp)


```

# JMJPFU
### 29-Mar-2017 

### Template 2 : Food / Restaurant

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

dissatRev <- dissatDf$badRev

# Step 2 : Creating the initial tdm

 dissatTdm <- tdmCreator(dissatRev[1:20]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 restdisTemp <- templateCreate(dissatTdm,'food',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

restdisTemp <- conTemplate(dissatRev,121,149,"food","restaurant",0.3,"freq6",restdisTemp)


```


### Template 3 : Staff

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

dissatRev <- dissatDf$badRev

# Step 2 : Creating the initial tdm

 dissatTdm <- tdmCreator(dissatRev[1:149]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 staffdisTemp <- templateCreate(dissatTdm,'staff',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

staffdisTemp <- conTemplate(dissatRev,101,149,"staff","NA",0.3,"freq3",staffdisTemp)


```


