---
title: "JMJPFU-Template"
output: html_notebook
---

# JMJPFU
### 29-Mar-2017

This is the OK template for all artefacts

## Artefacts for a hotel

Room: roomokTemp
Food: resokTemp
Restaurant: resokTemp
Staff: staffokTemp
Lobby: lobbyokTemp 
Reception: recepokTemp
Transfer: tranokTemp : No data
Facilities:facilokTemp
Recommend: reccokTemp : No data

### Initial tasks : Loading the library files

```{r}
library(SnowballC)
library(RWeka)
library(rJava)
library(RWekajars)
library(tm)

```

### Template 1 : Room

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

okRev <- okDf$badRev

# Step 2 : Creating the initial tdm

 okTdm <- tdmCreator(okRev[1:20]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 roomokTemp <- templateCreate(okTdm,'room',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

roomokTemp <- conTemplate(okRev,21,33,"room","rooms",0.3,"freq1",roomokTemp)

```


### Template 2 : Food/Restaurant

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

okRev <- okDf$badRev

# Step 2 : Creating the initial tdm

 okTdm <- tdmCreator(okRev[1:20]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 resokTemp <- templateCreate(okTdm,'food',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

resokTemp <- conTemplate(okRev,21,33,"food","restaurant",0.3,"freq1",resokTemp)

```


### Template 3 : Staff

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

okRev <- okDf$badRev

# Step 2 : Creating the initial tdm

 okTdm <- tdmCreator(okRev[1:20]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 staffokTemp <- templateCreate(okTdm,'staff',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

staffokTemp <- conTemplate(okRev,21,33,"staff","NA",0.3,"freq1",staffokTemp)

```

### Template 4 : Lobby

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

okRev <- okDf$badRev

# Step 2 : Creating the initial tdm

 okTdm <- tdmCreator(okRev[1:20]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 lobbyokTemp <- templateCreate(okTdm,'lobby',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

lobbyokTemp <- conTemplate(okRev,21,33,"lobby","NA",0.3,"freq1",lobbyokTemp)

```

### Template 5 : Reception

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

okRev <- okDf$badRev

# Step 2 : Creating the initial tdm

 okTdm <- tdmCreator(okRev[1:20]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 recepokTemp <- templateCreate(okTdm,'reception',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

recepokTemp <- conTemplate(okRev,21,33,"reception","NA",0.3,"freq1",recepokTemp)

```

### Template 6 : Transfer

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

okRev <- okDf$badRev

# Step 2 : Creating the initial tdm

 okTdm <- tdmCreator(okRev[1:33]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 tranokTemp <- templateCreate(okTdm,'transfer',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

tranokTemp <- conTemplate(okRev,21,33,"transfer","NA",0.3,"freq1",tranokTemp)

```


### Template 7 : Facility

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

okRev <- okDf$badRev

# Step 2 : Creating the initial tdm

 okTdm <- tdmCreator(okRev[1:20]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 facilokTemp <- templateCreate(okTdm,'facility',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

facilokTemp <- conTemplate(okRev,21,33,"facility","facilities",0.3,"freq1",facilokTemp)

```

### Template 8 : Recommend

### Process 1 : Initial template setting

```{r}

# Step 1 : Getting the review data in list format

okRev <- okDf$badRev

# Step 2 : Creating the initial tdm

 okTdm <- tdmCreator(okRev[1:33]) #  is selected because, this was the first list which had some words associated with staff
 
 # Step 3 : Creating the initial template
 
 reccokTemp <- templateCreate(okTdm,'recommend',0.30)


```

### Process 2 : Adding on to the initial template


```{r}

reccokTemp <- conTemplate(okRev,21,33,"recommend","NA",0.3,"freq1",reccokTemp)

```
